Detecting Facial Expressions in Professional Tennis Matches

### 2017-06-27 Report06-12.Rmd
Auto stash before merge of "master" and "steffMVP/master"

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(imager)
library(devtools)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(tidyverse)
library(magick)
library(kfigr)
library(UpSetR)
library(descr)
library(tables)
library(xtable)

@@

SignificancePlot <- function(model, data = GlmModelEstimates(model)) {
  data %>%
  mutate(significant = `Pr(>|z|)` < 0.05) %>%
  mutate(`Pr(<|z|)` = 1 - `Pr(>|z|)`) %>%
  ggplot(aes(x=type, y=`Pr(<|z|)`)) +  
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  geom_col(aes(fill=significant)) + 
  facet_wrap(~ variable)
}

EstimatesPlot <- function(model, data = GlmModelEstimates(model)) {
  data %>%
  mutate(significant = `Pr(>|z|)` < 0.05) %>%
  ggplot(aes(x=type, y=Estimate)) +  
  theme(axis.text.x = element_text(angle = 30, hjust = 1), 
        axis.text.y = element_text(angle = 30, hjust = 1)) +
  geom_col(aes(fill=significant)) + 
  facet_wrap(~ variable, scales = "free_y")
}

@@

A stepwise method was used to determin the best regression model for predicting a hit or miss. The regression model that provided the best AIC, included the scene attributes: Shot Angle, Back Ground, the interaction between these two; whether the scene was a graphic, and the situation on the court when the image was taken.
It also included the lighting on the particular face, and whether the specific face was accessorised with Glasses and a Visor or Hat.

>>>>

```{r cache=FALSE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
#packages:
library(bookdown)
library(pander)
library(ggplot2)
library(imager)
library(devtools)
library(knitcitations)
library(RefManageR)
library(readr)
library(knitr)
library(grid)
library(tidyverse)
library(magick)
library(kfigr)
library(UpSetR)
library(descr)
library(tables)
library(xtable)
library(ggthemes)
library(EBimage)

@@

SignificancePlot <- function(model, data = GlmModelEstimates(model)) {
  data %>%
  mutate(significant = `Pr(>|z|)` < 0.05) %>%
  mutate(`Pr(<|z|)` = 1 - `Pr(>|z|)`) %>%
  ggplot(aes(x=type, y=`Pr(<|z|)`)) +
  geom_col(aes(fill=significant)) + 
  facet_wrap(~ variable) +
  coord_flip()
}

EstimatesPlot <- function(model, data = GlmModelEstimates(model)) {
  data %>%
  mutate(significant = `Pr(>|z|)` < 0.05) %>%
  ggplot(aes(x=type, y=Estimate)) +
  geom_col(aes(fill=significant)) + 
  facet_wrap(~ variable) +
  coord_flip()
}

@@

A stepwise method was used to determin the best regression model for predicting a hit or miss. The regression model that provided the best AIC, included the scene attributes: Shot Angle, Background, the interaction between these two; whether the scene was a graphic, and the situation on the court when the image was taken.
It also included the lighting on the particular face, and whether the specific face was accessorised with Glasses and a Visor or Hat.
